Effects of epidemiological structure on the transient evolution of HIV virulence

### 2017-01-05 ms/cover_letter/plosHIVcover_resubm2.tex
working on resubm (text & cover ...)

\newcommand{\revcomment}[1]{\emph{#1}}
\newcommand{\response}[1]{#1}

@@

\revcomment{
Confusing sentence “ …in studies of discordant couples (…), HIV virulence as measured by the rate of progression to AIDS was both heritable and covaried with the set-point viral load (..) and the probability of transmission”.
- You are combining results of multiple different studies here. I don’t think there is a study that compared rate of progression to AIDS with probability of transmission. I think studies have a) compared SPVL to rate of progression, b) showed that SPVL was heritable, c) compared SPVL to probability of transmission. I think b) and c) required studying serodiscordant couples but I don’t think most studies of a) did.
}
\revcomment{
The paragraphs starting at line 40 read like methods, not introduction
}

@@

>>>>

\newcommand{\revcomment}[1]{\emph{#1}}
\newcommand{\response}[1]{#1}
\newcommand{\rzero}{\ensuremath{\mathcal R}_0}

@@

\response{
We were indeed thinking of reproduction \emph{rates} (i.e., $r$) rather than $\rzero$ here; we may be slightly more
attuned to $r$ because of our eco-evolutionary work, but we agree that it's clearer to start out with an $\rzero$
framing, which will be more familiar to technical readers (and clarifying the $r$-$\rzero$ distinction is really too much to try to pack into the first few sentences of the introduction).
}

\revcomment{
Confusing sentence “ …in studies of discordant couples (…), HIV virulence as measured by the rate of progression to AIDS was both heritable and covaried with the set-point viral load (..) and the probability of transmission”.
- You are combining results of multiple different studies here. I don’t think there is a study that compared rate of progression to AIDS with probability of transmission. I think studies have a) compared SPVL to rate of progression, b) showed that SPVL was heritable, c) compared SPVL to probability of transmission. I think b) and c) required studying serodiscordant couples but I don’t think most studies of a) did.
}

\response{
This is a good point. We have clarified the text here.
}

\revcomment{
The paragraphs starting at line 40 read like methods, not introduction
}

\response{
We think some of this material is useful to foreshadow what we're
going to do in the body of the paper, but we have trimmed the
technical details.
}

@@

\response{We have changed this term to ``contact structure'' throughout.}
